### 2014-04-16 paper.tex
More changes

@@

\section{DARPA Robotics Challenge}
\paragraph{The objective of this paper is to help the reader understand the current workings of the Carnegie Mellon’s University’s controller.}

The DARPA Robotics Challenge (DRC) is a competition of teams developing robots capable of assisting humans in responding to natural and man-made disasters.

Teams are spread in several tracks. WPI is in the Track C team, in which competed in the Virtual Challenge (DVC), and received funding for the Atlas robot.

The Atlas robot is a powerful robot in the form of an adult human. It is powered by 28 hydraulically-actuated rotation joints, with a closed-loop position and force control. It also contains a real time control computer (What is the specs?). Currently powered by external electricity, and packed with a head-mounted sensor package with LIDAR and stereo cameras.

MoveIt! is a software developed with ROS to help robot developers control the robot. It contains a inverse kinematics solver that can interface with Atlas, but prevents two containing limitations: 
\begin{inparaenum}[\itshape a\upshape)]
\item The inverse kinematics solver has no option to give approximate solutions, and will fail to give joint state values unless a very approximate solution for a desired hand position exists.
\item It does not account for modifying the pelvis position and orientation for solving for a solution. \end{inparaenum}

\section{Full-body controller}
Intro...Carnegie Mellon University developed custom software for controlling the robot, which involves two major aspects that are solve using Quadratic programming, an Inverse Kinematics solver, and an Inverse Dynamics solver.

\subsection{Inverse Kinematics}
Inverse kinematics is the process of given an desired end effector position, generate a joint state that will as close as possible achieve the goal. There exists a great deal of research, and libraries that provide fast and concise solutions, but most of the research assumes that the base of the joint system does not move, such as one that you might find on a factory.

The challenge of the system is to provide the correct weights for each the competing jacobians such that the robot is able to perform the desired motions while keeping balance, and smooth motions. For example, one might decrease the weight of the center of mass, thus allowing the arms to reach farther out, but at the same time it would allow the robot to more easily enter undesired configurations that might cause it to fall over.

>>>>

%%%% TODO: OVERALL INTRO %%%%
% Discuss the problem
% Section 1 talks about..sections 2, etc...

\section{Introduction}

In this paper we discuss the Worcester Polytechnic Institute and a team at Carnegie Mellon University use the Boston Dynamics Atlas robot at the DARPA Robotics Challenge (DRC). Initially we will discuss about the tasks involved in the challenge, and the hardware specifications and limitations. We will then progress to the software architecture and the mathematics behind the controller.

\section{DARPA Robotics Challenge}
%\paragraph{The objective of this paper is to help the reader understand the current workings of the Carnegie Mellon’s University’s controller.}

The DARPA Robotics Challenge (DRC) is a competition of teams developing robots capable of assisting humans in responding to natural and man-made disasters. The goal of the DRC is to design a robust robotic system that has mobility and dexterity in disaster zones, the ability to use tools designed for humans, and supervised autonomy.

Teams are spread in several tracks. Worcester Polytechnic Institute is in the Track C team, in which competed in the Virtual Challenge (DVC), and received funding for the Atlas robot.

As described by the Atlas Robot Operation and Maintenance Manual, "The Atlas robot’s on-board features include a real time computer, a hydraulic power pack, force/torque sensors, inertial sensing, and active thermal management. In addition to the integrated sensors, the Atlas robot comes equipped with the MultiSense-SL sensor head from Carnegie Robotics, and modular wrists"

WARNER is 6 foot 2 inches tall and weighs approximately 330 pounds. The movement is powered by 28 hydraulically-actuated rotation joints, with a closed-loop position and force control.

\subsection{Sensors}

For external sensors Atlas has:

\subsubsection{Carnegie Robotics Sensor Head}
\begin{wrapfigure}{r}{0.25\textwidth}
  \begin{center}
    \includegraphics[scale=0.25]{images/sensorhead.jpg}
  \end{center}
  \caption{Multisense SL}
\end{wrapfigure}

The MultiSense SL is a tri-modal range sensor, priving laser range data, stereo range data, and video output stream. The device provides the majority of perceptual data used for teleoperation as well as automated control.

The apparatus brings together a Hokuyo UTM-30LX-EW laser, which output 43,000 points per second, and a Carnegie Robotics MultiSense S7 high resolution stereo camera, with a 4 megapixels on each side.  On-board processing handles image rectification, stereo data processing, time synchronizing of laser data with a spindle encoder, spindle motor control, and lighting timing. \cite{multisense-sl}

\subsubsection{Situational awareness cameras}

Two Situational awareness cameras are placed just below the head of the robot, providing a wide range view of the workspace.

\begin{figure}[ht]
\begin{center}
\begin{minipage}[b]{0.4\linewidth}
\centering
\includegraphics[width=\textwidth]{images/sitcamFOV.png}
\caption{Top-down view of the robot, display range of view}
\label{fig:figure1}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.4\linewidth}
\centering
\includegraphics[width=\textwidth]{images/fisheye.jpg}
\caption{View of the camera}
\label{fig:figure2}
\end{minipage}
\end{center}
\end{figure}

%%%% MOVE OUT OF HARDWARE%%%%%
MoveIt! is a software developed with ROS to help robot developers control the robot. It contains a inverse kinematics solver that can interface with Atlas, but prevents two containing limitations: 
\begin{inparaenum}[\itshape a\upshape)]
\item The inverse kinematics solver has no option to give approximate solutions, and will fail to give joint state values unless a very approximate solution for a desired hand position exists.
\item It does not account for modifying the pelvis position and orientation for solving for a solution. \end{inparaenum}

\section{Full-body controller}
% further discuss the need fo a full-body controller,
Intro...Carnegie Mellon University developed custom software for controlling the robot, which involves two major aspects that are solve using Quadratic programming, an Inverse Kinematics solver, and an Inverse Dynamics solver.

% Intro to all the following sections ( basically a summary)
% IK ID QP

\subsection{Inverse Kinematics}

% Discuss why there are infinite solutions
% Algorithms can therefore optimize for certain criteria
% Our approach uses QP with Jacobian stacking

Inverse kinematics is the process of given an desired end effector position, generate a joint state solution for that goal. There exists a great deal of research, and libraries that provide fast and concise solutions, but most of the research assumes that the base of the joint system is stationary, such as one that you might find on industrial manipulators.

Therefore most research in this field does not take into account stability of the robot. Which is a priority in the case of a bipedal robot such as Atlas.

The challenge of the system is to provide the correct weights for each the competing Jacobians such that the robot is able to perform the desired motions while keeping balance, and smooth motions. For example, one might decrease the weight of the center of mass, thus allowing the arms to reach farther out, but at the same time it would allow the robot to more easily enter undesired configurations that might cause it to fall over.

@@
